\vspace{5cm} \normalsize \textsc{\NetIDb} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{\documenttitle}} \HRule{2pt} \\ [0.5cm] \normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\ }\normalsize \vspace*{5\baselineskip}

### 2025-03-24 Manuscript/Plantilla memòria TFG 2024_25.tex
Writting

\newacronym{cox2}{COX-2}{Cyclooxygenase-2}
\newacronym{ptgs2}{PTGS2}{Prostaglandin-endoperoxide synthase 2}
\newacronym{ai}{AI}{Artificial intelligence}
\newacronym{ml}{ML}{Machine Learning}
\newacronym{rf}{RF}{Random Forest}
\newacronym{id}{ID}{Identificator}
\newacronym{ic50}{IC$_{50}$}{Half maximal inhibitory concentration}
\newacronym{ic90}{IC$_{90}$}{90 percent inhibitory concentration}
\newacronym{ic99}{IC$_{99}$}{99 percent inhibitory concentration}
\newacronym{tp}{TP}{True Posive}
\newacronym{fp}{FP}{False Posive}
\newacronym{tn}{TN}{True Negative}
\newacronym{fn}{FN}{False Negative}

@@

 Although significant advancements have been made, cancer still accounts for over 8 million deaths per year worldwide, and the scientific and medical communities remain far from achieving its complete eradication. Inflammation is one of the hallmarks of carcinogenesis; in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences. When a tissue is damaged, inflammation protects the organism from infections caused by external pathogens, a key function of the immune system to prevent the presence of invaders in the body. During the inflammatory process, cells proliferate under the command of the immune system to replace the damaged cells of the affected tissue. However, if this cell reproduction continues beyond the healing of the damaged tissue, it can potentially lead to cancer, contradicting the initial healing purpose of the inflammatory process. In some cases, inflammation can become chronic, leading to tumor development and uncontrolled cell proliferation. As a result, a wide range of drug prototypes have been designed to suppress inflammation. However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications. Consequently, the administration of these drugs is often counterproductive, and the search for a more effective and safer treatment remains ongoing.

>>>>

\newacronym{cox2}{COX-2}{Cyclooxygenase-2}
\newacronym{nsaid}{NSAID}{Non-Steroidal Anti-Inflammatory Drug}
\newacronym{ptgs2}{PTGS2}{Prostaglandin-endoperoxide synthase 2}
\newacronym{ai}{AI}{Artificial intelligence}
\newacronym{ml}{ML}{Machine Learning}
\newacronym{rf}{RF}{Random Forest}
\newacronym{id}{ID}{Identificator}
\newacronym{ic50}{IC$_{50}$}{Half Maximal Inhibitory Concentration}
\newacronym{ic90}{IC$_{90}$}{90 Percent Inhibitory Concentration}
\newacronym{ic99}{IC$_{99}$}{99 Percent Inhibitory Concentration}
\newacronym{tp}{TP}{True Posive}
\newacronym{fp}{FP}{False Posive}
\newacronym{tn}{TN}{True Negative}
\newacronym{fn}{FN}{False Negative}

@@

Although significant advancements have been made, cancer still accounts for over 8 million deaths per year worldwide, and the scientific and medical communities remain far from achieving its complete eradication. Inflammation is one of the hallmarks of carcinogenesis; in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences. When a tissue is damaged, inflammation protects the organism from infections caused by external pathogens, a key function of the immune system to prevent the presence of invaders in the body. During the inflammatory process, cells proliferate under the command of the immune system to replace the damaged cells of the affected tissue. However, if this cell reproduction continues beyond the healing of the damaged tissue, it can potentially lead to cancer, contradicting the initial healing purpose of the inflammatory process. In some cases, inflammation can become chronic, leading to tumor development and uncontrolled cell proliferation. As a result, a wide range of drug prototypes have been designed to suppress inflammation. However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications. Consequently, the administration of these drugs is often contrindicative, and the search for a more effective and safer treatment remains ongoing. Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process, subsequently, a therapy based on the he chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.

The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. In this project we do focus on the \gls{ic50}.

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. One of the best drug candidates is
